### 2017-01-07 paper/evaluation.tex
updated eval

Given that 19.3\% of the projects (\ie, 61 projects) are costly,
we concluded that time-consuming regression test suites are relatively
frequent in open-source projects.  It is important to mention that
Figure~\ref{fig:rq1-barplot} represents a lower bound for time cost:
some tests may finish early due to a failure since the subjects were
tested in a potentially unstable revision. \Jbc{How many executed
completely? From the failed subjects, how much of the test suite was
executed?}

>>>>

Given that 19.3\% of the projects (\ie, 82 projects) are costly,
we concluded that time-consuming regression test suites are relatively
frequent in open-source projects.  It is important to mention that
Figure~\ref{fig:rq1-barplot} represents a lower bound for time cost:
some tests may finish early due to a failure since a subject may be
tested in a potentially unstable revision. From the \numSubjs{}
projects, 286 passed all tests and 118 had failures.
